Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-26 inst/surfing_jsa_rebuttal_minorcomments.tex

Page 17: Figure 2 caption is a little brief and could better explain
what is observed in the plot (e.g. the positive correlation between
variables). Especially as the authors have distorted the x-axis and
fitted a linear trend through the data. What is the reason for this?
As mentioned in a previous comment, I’d prefer to see the x-axis in
its raw form, unless there is a reason it has been distorted.

\textcolor{blue}{More detail added in caption}

Page 18: Figure 3 title – this doesn’t provide the reader with any
additional information. It does seem a little odd that Figure 2 does
not have a title, Figure 3 does, and Figure 4 does not. For
consistency, the authors could simply remove the title from Figure 33,
as it does not really add any value.

\textcolor{blue}{Done (title removed from figure 3 as suggested)}

@@

Page 19: Figure 4 Capitalisation of y-axis title.  General comment:
should the Table and Figure captions have a full-stop at the end of
the last sentence?

\textcolor{blue}{Done.  Looking at recent JSA articles the captions do
  not have full-stops and we just copied that style}

General comment: As part of a potential future publication in the
field, I'd be curious to see the methodology in Section 7 applied to
World Surf League data from events that occurred prior to the
announcement that surfing would be in the Olympics.  Comparing these
results with those in the paper that use data from after this
announcement (perhaps supplemented with additional data and results
from post-2019), would help in our understanding whether there truly
has been an observable change in non-competitive behaviour between
compatriots.  Any such analysis is clearly well beyond the realm of
minor revisions and is not something I expect of the authors prior to
final submission; however, I thought it could be an interesting next
step for the application of the methodology outlined in the paper!

\textcolor{blue}{This suggestion is an excellent one (which had not
  occurred to us); as remarked, it is not in scope for the current
  paper.  We do plan to work on this idea in the future and have added
  a brief discussion to the ``Future work'' section
}

### 2022-09-26 inst/surfing_jsa.tex
fixes #180
issue #167

\citet{farley2013} analyse surfing results using
one-way ANOVA techniques and report comparisons between the top 10 and
bottom 10 surfers in the 2013 WSL tour and conclude
that the top-ranked athletes are more consistent than the lower-ranked
group.  They report that ``to date, only a limited number of research
studies have reported on the results of competitive surfing" [p44],
and the analysis presented here fills some of this gap.

@@

Further work might include incorporation of more tournament results
into our likelihood function, and possibly to investigate priority
infringements between compatriots.

>>>>

\citet{farley2013} analyse surfing results using
one-way ANOVA techniques and report comparisons between the top 10 and
bottom 10 surfers in the 2013 World Championship Tour (WCT) and conclude
that the top-ranked athletes are more consistent than the lower-ranked
group.  They report that ``to date, only a limited number of research
studies have reported on the results of competitive surfing" [p44],
and the analysis presented here fills some of this gap.

@@

Further work might include incorporation of more tournament results
into our likelihood function, and possibly to investigate priority
infringements between compatriots.  One suggestion, made by an
anonymous JSA referee, was to apply the methodology used in Section 7
to events that occurred prior to the announcement that surfing would
be in the Olympics.  This would allow the quantification of any {\em
  change} in non-competitive behaviour between compatriots.
